Bibat: Batteries-include Bayesian Analysis Template

### 2024-02-15 paper/main.qmd
Update paper

Bibat integrates many widely-adopted, open-source and powerful tools to
implement the components of a Bayesian workflow. Bibat projects are is
written in modern Python and uses pydantic @pydanticdevelopersPydantic2022
and pandera [@niels_bantilan-proc-scipy-2020] for data modelling, Stan
[@carpenterStanProbabilisticProgramming2017] for statistical inference,
cmdstanpy [@standevelopmentteamCmdStanPy2022] for python-Stan interface, arviz
[@kumarArviZUnifiedLibrary2019] for storing and analyzing inferences and sphinx
[@georgbrandlandthesphinxteamSphinx2022] and quarto [@Allaire_Quarto_2022]
for documentation.  Bibat itself is also written in modern Python and uses the
popular tools cookiecutter [@greenfeldCookiecutter2021], pydantic and click
[@clickdevelopersClickPythonComposable2022].

To encourage collaborative development of Bayesian workflow projects, Bibat
projects include a preconfigured test environment, continuous integration,
linting and pre-commit hooks. In addition, including documentation as a
first class component of the analysis addresses a common problem in academic
statistics projects where the paper gets out of sync with the code. Bibat itself
is continuously tested to ensure that it works on the operating systems Linux,
macOS and Windows. Bibat's continuous integration runs a test suite as well as
an end-to-end functional test on all supported Python versions.

@@

Bibat is developed in public and encourages community contribution. Please see the contributing page <https://github.com/teddygroves/bibat/blob/main/CONTRIBUTING.rst> and code of conduct <https://github.com/teddygroves/bibat/blob/main/CODE_OF_CONDUCT.md> if you would like to help develop bibat.

>>>>

Bibat integrates many widely-adopted, open-source and powerful tools to
implement the components of a Bayesian workflow. Bibat projects are  written
in modern Python and uses pydantic [@pydanticdevelopersPydantic2022]
and pandera [@niels_bantilan-proc-scipy-2020] for data modelling, Stan
[@carpenterStanProbabilisticProgramming2017] for statistical inference,
cmdstanpy [@standevelopmentteamCmdStanPy2022] for python-Stan interface, arviz
[@kumarArviZUnifiedLibrary2019] for storing and analyzing inferences and sphinx
[@georgbrandlandthesphinxteamSphinx2022] and quarto [@Allaire_Quarto_2022]
for documentation.  Bibat itself is also written in modern Python and uses the
previously mentioned software as well as the popular  popular template tool
copier [@copierdevelopersCopier2024].

To encourage collaborative development of Bayesian workflow projects, Bibat
projects include a preconfigured test environment, continuous integration,
linting and pre-commit hooks. In addition, including documentation as a
first class component of the analysis addresses a common problem in academic
statistics projects where the paper gets out of sync with the code. Bibat is
continuously tested to ensure that it works on the operating systems Linux,
macOS and Windows. Bibat's continuous integration runs a test suite as well as
an end-to-end functional test on all supported Python versions.

@@

Bibat is developed in public and encourages community contribution. Please see the contributing page <https://github.com/teddygroves/bibat/blob/main/CONTRIBUTING.md> and code of conduct <https://github.com/teddygroves/bibat/blob/main/CODE_OF_CONDUCT.md> if you would like to help develop bibat.
